---
title: "Assignment 3 DATA 607"
author: "Neil Hodgkinson"
date: "2022-09-18"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library (readr)
library(stringr)
library(tidyverse)

urlfile="https://raw.githubusercontent.com/Nhodgkinson/data/master/college-majors/majors-list.csv"

mydata<-read_csv(url(urlfile))


```

## Exercise 1

```{r ex1}
maj <- str_detect(string=mydata$Major, "DATA|STATISTICS", negate=FALSE)
mydata[maj, c("Major")]
```

## Exercise 2

"bell pepper"  "bilberry"     "blackberry"   "blood orange"

"blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

 "elderberry"   "lime"         "lychee"       "mulberry"    

 "olive"        "salal berry"

```{r ex2}

str_c(fruit, collapse = "', '")

```


## Exercise 3

    (.)\1\1 : Matches any 3 like characters in a row
    "(.)(.)\\2\\1" : Matches 2 seperate characters that repeat in reverse order
    (..)\1 :  2 characters that repeat
    "(.).\\1.\\1" : matches a character the repeats after another character. 
    "(.)(.)(.).*\\3\\2\\1" : three characters followed by any number of characters tailed by the original 3 characters in reverse


## Exercise 4

```{r ex4}
#Start and end with the same character.
str_subset(fruit, "^(.)((.*\\1$)|\\1?$)")

#Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
str_subset(fruit, "([A-Za-z][A-Za-z]).*\\1")

#Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
str_subset(fruit, "([a-z]).*\\1.*\\1")

```

